
## INSIDER

**INSIDER** are TE assembled on genome

### NUMBER OF TE

#### INSERTION

Total number of **TE : `r data=read.csv("../../INSIDER/TE_DETECTION/INSERTION.csv", sep="\t"); nrow(data);`**

Number of family found : **`r data=read.csv("../../INSIDER/TE_DETECTION/INSERTION_COUNT_TE.csv", sep="\t"); nrow(data);`**

```{r insider1, eval=TRUE, include=TRUE, results=TRUE, out.width="90%"}

data = read.csv("../../INSIDER/TE_DETECTION/INSERTION_COUNT_TE.csv", sep="\t")
#kbl(data)

data = tail(data, 50)


uniqy = unique(data$y)
uniqx = unique(data$x)

for (y in uniqy)
{
  datay = data[data$y %in% y, ]
  for(x in uniqx){
    datax = datay[datay$x %in% x, ]
    if(nrow(datax) != 1){
      new_line_data <- data.frame(x, y, 0)
      names(new_line_data) <- c("x", "y", "z")

      data <- rbind(data, new_line_data)
    }
  }
}


max=0
namx=""
for(x in uniqx){
  datax = data[data$x %in% x, ]
  if(max(datax$z)>max){
    max  = max(datax$z)
    namx = x
  }
}

datax = data[data$x %in% namx, ]
datax = datax[order(datax$z), ]

data$y <- factor(data$y, levels = datax$y)

nb_diff_TE = length( unique(data$y) )

xlabel = ''
graph <- ggplot(data, aes(x, y, fill=z, width=0.95, height=0.95)) + 
    geom_tile() + 
    ggtitle("") +
    
    theme(axis.text.x = element_blank(), axis.text.y = element_text(face="plain", color="#222222", size=6, angle=0)) +
    coord_fixed() +
    scale_fill_gradientn(colours=brewer.pal(n= 9, name="Reds")) +
    #scale_fill_viridis(option="heat") +
theme(panel.background = element_rect(fill = "white", colour = "grey", size=0)
  #,panel.border = element_rect(linetype = "dashed", fill = NA)
  #, panel.grid.major = element_line(colour = "black")
) +
geom_segment( aes(x = 5, y = 1, xend = 5, yend = nb_diff_TE ), colour = "black", alpha=0, size=0.9 , inherit.aes = FALSE , linetype="twodash") +

    labs(y="TE", x=xlabel, fill="NUMBER OF TE") +
geom_text(aes(label = z), nudge_x=1.2, color = "#222222", size = 2) 

order_TE = data$y

#graph
graph
#ggsave(name_output)

```

<iframe src="lib/template_COUNT_TE_INSIDER.html" style="width: 100%; height: 1000px; border: none; overflow: hidden;"></iframe>

hover your mouse over the bars or navigate with the slider if the number of different TE families is greater than 20


#### DELETION

Total number of **TE : `r data=read.csv("../../INSIDER/TE_DETECTION/DELETION.csv", sep="\t"); nrow(data);`** <!-- TE_INSIDER_DEL -->

Number of family found : **`r data=read.csv("../../INSIDER/TE_DETECTION/DELETION_COUNT_TE.csv", sep="\t"); nrow(data);`** <!-- TE_INSIDER_DEL -->


```{r insider11, eval=TRUE, include=TRUE, results=TRUE, out.width="90%"}

data = read.csv("../../INSIDER/TE_DETECTION/DELETION_COUNT_TE.csv", sep="\t")
#kbl(data)

data = tail(data, 50)


uniqy = unique(data$y)
uniqx = unique(data$x)

for (y in uniqy)
{
  datay = data[data$y %in% y, ]
  for(x in uniqx){
    datax = datay[datay$x %in% x, ]
    if(nrow(datax) != 1){
      new_line_data <- data.frame(x, y, 0)
      names(new_line_data) <- c("x", "y", "z")

      data <- rbind(data, new_line_data)
    }
  }
}


max=0
namx=""
for(x in uniqx){
  datax = data[data$x %in% x, ]
  if(max(datax$z)>max){
    max  = max(datax$z)
    namx = x
  }
}

datax = data[data$x %in% namx, ]
datax = datax[order(datax$z), ]

data$y <- factor(data$y, levels = datax$y)

nb_diff_TE = length( unique(data$y) )

    #print("ok--s")
xlabel = ''
graph <- ggplot(data, aes(x, y, fill=z, width=0.95, height=0.95)) + 
    geom_tile() + 
    ggtitle("") +
    
    theme(axis.text.x = element_blank(), axis.text.y = element_text(face="plain", color="#222222", size=6, angle=0)) +
    coord_fixed() +
    scale_fill_gradientn(colours=brewer.pal(n= 9, name="YlGnBu")) +
    #scale_fill_viridis(option="heat") +
theme(panel.background = element_rect(fill = "white", colour = "grey", size=0)
  #,panel.border = element_rect(linetype = "dashed", fill = NA)
  #, panel.grid.major = element_line(colour = "black")
) +
geom_segment( aes(x = 5, y = 1, xend = 5, yend = nb_diff_TE ), colour = "black", alpha=0, size=0.9 , inherit.aes = FALSE , linetype="twodash") +


    labs(y="TE", x=xlabel, fill="NUMBER OF TE") +
geom_text(aes(label = z), nudge_x=1.2, color = "#222222", size = 2) 

order_TE = data$y

graph

```


<iframe src="lib/template_COUNT_TE_INSIDER_DEL.html" style="width: 100%; height: 1000px; border: none; overflow: hidden;"></iframe>

hover your mouse over the bars or navigate with the slider if the number of different TE families is greater than 20 <!-- TE_INSIDER_DEL -->



### FREQUENCE


```{bash FREQB2, eval=TRUE, include=TRUE, results=TRUE}

test -s ../../INSIDER/FREQ_GLOBAL/DEPTH_TE_INSIDER.csv && python3 ../lib/freq_graph.py ../../INSIDER/FREQ_GLOBAL/DEPTH_TE_INSIDER.csv FREQ_TE.csv || echo ;

```



```{r FREQIN, eval=TRUE, include=TRUE, results=FALSE, out.width="90%", echo=FALSE}

data = read.csv("FREQ_TE.csv", sep="\t")
data = tail(data, 50)

data$x <- factor(data$x, levels = order_TE)

#orderc = order frequence
order <- read.table("orderc.txt", header = FALSE)
data$condition <- factor(data$condition, levels = order$V1)

p = ggplot(data, aes(fill=condition, y=y, x=x)) + 
        geom_bar(position="stack", stat="identity") +
        xlab("TE") +
        ylab("NUMBER") +
        labs(fill = "FREQUENCE") +
        #scale_fill_viridis(discrete = T) +
        scale_fill_manual(values=brewer.pal(n = length(unique(data$condition)), name="Reds")) +
        theme(axis.text.x = element_text(face="plain", color="#222222", size=10, angle=90, vjust=0.5),
            panel.background = element_rect(fill="white", colour="white", 
                                          linetype="solid", color="white"))

p
#ggsave(p, file=output)

```


### TSD

```{bash, eval=TRUE, include=TRUE, results=TRUE}

grep "OK" ../../VALUES_TSD_INSIDER_GROUP.csv | awk 'BEGIN{somme=0}{somme+=$2}END{print somme}' > .tmp_TE_TSD_OK.txt || echo "ERROR TSD"

grep "KO" ../../VALUES_TSD_INSIDER_GROUP.csv | awk 'BEGIN{somme=0}{somme+=$2}END{print somme}' > .tmp_TE_TSD_KO.txt || echo "ERROR TSD"

awk 'BEGIN{somme=0} NR>1 {somme+=$2}END{print somme}' ../../VALUES_TSD_INSIDER_GROUP.csv > .tmp_TE_TSD_TOTAL.txt || echo "ERROR TSD"

```

TSD [OK] : these are the TE with TSD **`r readLines(".tmp_TE_TSD_OK.txt");`/`r readLines(".tmp_TE_TSD_TOTAL.txt");`**

TSD [KO] : these are the TE without TSD **`r readLines(".tmp_TE_TSD_KO.txt");`/`r readLines(".tmp_TE_TSD_TOTAL.txt");`**

<iframe src="lib/template_TSD_INSIDER_histo.html" style="width: 100%; height: 700px; border: none; overflow: hidden;"></iframe>

Hover your mouse over the bars or navigate with the slider if the number of different TE families is greater than 20

### TE POSITION

<iframe src="lib/template_COUNT_TE_GENOME_CIRCOS_INSIDER.html" style="width: 100%; height: 700px; border: none; overflow: hidden;"></iframe>

Select TE family


<!-- remove inutile fiels -->

```{bash, eval=TRUE, include=TRUE, results=TRUE}


rm -f FREQ_TE.csv
rm -f .tmp_*


```